Supplementary Information: Global patterns of forest autotrophic carbon fluxes

### 2020-06-13 manuscript/appendix.Rmd
remove FACF abbreviation from appendix.Rmd
#74

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S5 <- read.csv("tables_figures/mat_map.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S5, format = "latex", booktabs = TRUE, caption = "Table S3. Results of analysis of interactions effects between MAT and MAP, for all FACF", escape = F)%>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12) %>%
  column_spec(1, width = "4cm") %>%
  column_spec(2, width = "6cm") %>%
  column_spec(3, width = "6cm") %>%
  column_spec(4, width = "6cm")%>%
  column_spec(5, width = "2cm")%>%
  column_spec(6, width = "2cm")
```

\newpage
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S2 <- read.csv("tables_figures/mat_growing_season.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S2, format = "latex", booktabs = TRUE, caption = "Table S4. Comparison of growing season length and mean annual temperature as predictors of FACF", escape = F)%>%
  kable_styling(latex_options = c("scale_down", "hold_position")) %>%
  column_spec(1, width = "5cm") %>%
  column_spec(2, width = "2cm") %>%
  column_spec(3:4, width = "7cm") %>%
  pack_rows("GPP", 1, 3, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("NPP", 4, 6, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("ANPP", 7, 9, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("ANPP woody stem", 10, 12, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("ANPP foliage", 13, 15, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("BNPP root", 16, 18, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("BNPP fine root", 19, 21, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("Autotrophic respiration", 22, 24, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("Root respiration", 25, 27, latex_gap_space = "1em", colnum = 1, hline_before = TRUE)
```

\newpage
```{r echo=FALSE, fig.cap = "Figure S1: Maps showing distribution of samples for the nine FACF analyzed here.", out.height ='95%', fig.pos='H'}

@@

\blandscape
```{r echo=FALSE, fig.align = "center", fig.cap = "Figure S2: Correlations among latitude and climate variables. Variable names and units given in Table S1", out.height='95%', fig.pos='H'}

@@

```{r echo=FALSE, fig.align = "center", fig.cap = "Figure S3: Ratios among FACF as a function of latitude and climate variables", out.width ='80%', fig.pos='H'}

@@

\blandscape
```{r echo=FALSE, fig.cap = "Figure S4: Individual plots of FACF in relation to mean annual climate, part 1.", out.height='95%', fig.pos='H'}

@@

```{r echo=FALSE, fig.cap = "Figure S5: Individual plots of FACF in relation to mean annual climate, part 2.", out.height='95%', fig.pos='H'}

@@

```{r echo=FALSE, fig.cap = "Figure S6: Individual plots of FACF in relation to mean climate seasonality, part 1.", out.height ='95%', fig.pos='H'}

@@

\newpage
```{r echo=FALSE, fig.cap = "Figure S7: Individual plots of FACF in relation to mean climate seasonality, part 2.", out.width ='100%', fig.pos='H'}

@@

\newpage
```{r echo=FALSE, fig.cap = "Figure S8: Growing season length-standardized FACF in relation to mean growing season climate, part 1.", out.width ='100%', fig.pos='H'}

@@

\newpage
```{r echo=FALSE, fig.cap = "Figure S9: Growing season length-standardized FACF in relation to mean growing season climate, part 2.", out.width ='100%', fig.pos='H'}

>>>>

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S5 <- read.csv("tables_figures/mat_map.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S5, format = "latex", booktabs = TRUE, caption = "Table S3. Joint effects of MAT and MAP on forest C fluxes", escape = F)%>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12) %>%
  column_spec(1, width = "4cm") %>%
  column_spec(2, width = "6cm") %>%
  column_spec(3, width = "6cm") %>%
  column_spec(4, width = "6cm")%>%
  column_spec(5, width = "2cm")%>%
  column_spec(6, width = "2cm")
```

\newpage
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S2 <- read.csv("tables_figures/mat_growing_season.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S2, format = "latex", booktabs = TRUE, caption = "Table S4. Comparison of growing season length and MAT as predictors of forest C fluxes", escape = F)%>%
  kable_styling(latex_options = c("scale_down", "hold_position")) %>%
  column_spec(1, width = "5cm") %>%
  column_spec(2, width = "2cm") %>%
  column_spec(3:4, width = "7cm") %>%
  pack_rows("GPP", 1, 3, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("NPP", 4, 6, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("ANPP", 7, 9, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("ANPP woody stem", 10, 12, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("ANPP foliage", 13, 15, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("BNPP root", 16, 18, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("BNPP fine root", 19, 21, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("Autotrophic respiration", 22, 24, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("Root respiration", 25, 27, latex_gap_space = "1em", colnum = 1, hline_before = TRUE)
```

\newpage
```{r echo=FALSE, fig.cap = "Figure S1: Maps showing distribution of samples for the nine forest C fluxes analyzed here", out.height ='95%', fig.pos='H'}

@@

\blandscape
```{r echo=FALSE, fig.align = "center", fig.cap = "Figure S2: Correlations among latitude and climate variables", out.height='95%', fig.pos='H'}

@@

```{r echo=FALSE, fig.align = "center", fig.cap = "Figure S3: Ratios among forest C fluxes as a function of latitude and climate variables", out.width ='80%', fig.pos='H'}

@@

\blandscape
```{r echo=FALSE, fig.cap = "Figure S4: Individual plots of forest C fluxes in relation to mean annual climate, part 1.", out.height='95%', fig.pos='H'}

@@

```{r echo=FALSE, fig.cap = "Figure S5: Individual plots of forest C fluxes in relation to mean annual climate, part 2.", out.height='95%', fig.pos='H'}

@@

```{r echo=FALSE, fig.cap = "Figure S6: Individual plots of forest C fluxes in relation to mean climate seasonality, part 1.", out.height ='95%', fig.pos='H'}

@@

\newpage
```{r echo=FALSE, fig.cap = "Figure S7: Individual plots of forest C fluxes in relation to mean climate seasonality, part 2.", out.width ='100%', fig.pos='H'}

@@

\newpage
```{r echo=FALSE, fig.cap = "Figure S8: Growing season length-standardized forest C fluxes in relation to mean growing season climate, part 1.", out.width ='100%', fig.pos='H'}

@@

\newpage
```{r echo=FALSE, fig.cap = "Figure S9: Growing season length-standardized forest C fluxes in relation to mean growing season climate, part 2.", out.width ='100%', fig.pos='H'}
